% Copyright Page
\thispagestyle{empty}
\vspace*{\fill}
\begin{center}
    Copyright \copyright\ 2026 by Nathaniel Ingle. \\

    \vspace{1em}

    % --- THE CREATIVE COMMONS NOTICE ---
    \ccbysa\ This work is licensed under the Creative Commons Attribution-ShareAlike 4.0 International License.\\
    To view a copy of this license, visit:\\
    \url{http://creativecommons.org/licenses/by-sa/4.0/}

    \vspace{1em}
    Cover art: Edward Weston, ``Pepper No. 30 (Colorized),'' 1930 \\ 
    Photograph, 24.1 $\times$ 19.2 cm. Public domain.\\ 
    \vspace{3em}
    This is a work of satire. The authors and opinions that appear in this volume are entirely fictional. Any resemblance to real-world events, people, or movements is entirely coincidental. DougDoug may or may not be real. Douglas Studies is only real insofar as this anthology has made it so.\\
\vspace{1.5em}
    % --- FAKE LIBRARY OF CONGRESS BLOCK ---
\begin{minipage}{0.9\textwidth} % Constrain width to look like a block
    \small % Use smaller font for that "fine print" look
    \setlength{\parskip}{0.2em}
    \setlength{\parindent}{0pt}
    
    Publisher's Catalogue-in-Publication Data\\
    
    \textit{Donations, Death Roads, and Dogs: An Anthology of Critical Douglas Studies} / edited by Nathaniel Ingle. -- Third Edition.
    
    \vspace{0.5em}
    p. cm. \\
    Includes bibliographical references and index. \\
    ISBN 979-8-2437-5214-5 (pbk.)
    
    \vspace{0.5em}
    1. Douglas Studies--Philosophy. 2. Streaming (Technology)--Social aspects. 3. Bell peppers in popular culture. 4. Divorce--Psychological aspects. 5. Baldness--Anecdotes. I. Ingle, Nathaniel, editor. II. Title.
    
    \vspace{0.5em}
    PN1992.8.S74 D68 2026 \hfill 302.23'1--dc23
\end{minipage}

\vspace{1.5em}

    ISBN: 979-8-2437-5214-5\\
\end{center}
\vspace*{\fill}
\newpage

