DougDoug has long been the subject of intense interest and speculation
not only amid Britain, Ireland, and the European content creators, but
worldwide. This interest has produced a treasure-trove of analysis,
contextualization, and healthy debate. The present volume owes
everything to the critics who laid the groundwork for this field of
inquiry. That said, what value does yet another addition to this already
crowded field provide? In truth there is nothing new or unique within
these pages. The editors have eschewed pursuing groundbreaking work for
the much more monumental task of selecting the ``best hits'' of an
already deeply controversial academic lineage.

Our hope is that by providing the essential texts, the best above the
rest, the student can gain immediate access to and appreciation of
Douglas Studies as a subject and theoretical framework. As the most
neglected branch of our embattled Humanities, Douglas Studies is
frequently called upon to ``prove'' its unique value and insight in a
world defined by career opportunities, stakeholder value, and fickle
undergraduate interests. That conversation then is endlessly complicated
by academics who cannot agree whether their subject's purpose consists
of cultivating the appreciation or the critical deconstruction of
``Douglas'' (itself a term whose definition is perpetually scrutinized,
displaced, and reconstructed). The present volume does not seek to
reconcile these divergent interpretations, but it does provide the
context and historical frameworks required to understand how these
differing interpretations arose and why they remain so entrenched and
uncooperative.

The present volume, above everything else, provides a stable foundation
for both a student's academic life and their own personal growth. These
timeless texts, chosen for their enduring quality and consistently
insightful voice across generations, will appeal to specialists and the
inquisitive general reader alike. It's also quite handsome when wrapped
up as a Christmas gift for every member of your friends and family.
