\begin{description}
	\item[Dr. B. B. Braille] works as a clinical psychologist for the Basement Hospital. His doctoral dissertation dealt with the application of psychoanalysis to the dreams of butterflies.

	\item[Brett Beubb] works as a full-time YouTuber. They release bi-annual videos on their YouTube channel \emph{You're Wrong About Everything}. Their most popular series is the playlist of three nine-minute videos titled \emph{A Complete Deconstruction of the Alternatively Awake's Arguments}. They hope to complete this series some time in 2039. 

	\item[Jean-François Cul-de-Sac] serves as the head deacon at Saint Rosa's Cathedral in Erehwon, California. He is currently working on a collection of poems entitled \emph{My Cup Runneth Over, For It Hath No Drinking Hole}.

	\item[Lucian Gregory] was born in 1875 and raised in a devout Presbyterian family. He published a series of anarchist poems advocating for the abolition of the British monarchy and disappeared during the German aerial bombing campaign some time around March, 1941.

	\item[Comrade Juliet Jepardi] is the chairwoman of the Marxist Fellowship of Proletariat Research for the Department of Economic Praxis, Rudyard University. She is a staunch advocate for the labor rights of emotional support animals.

	\item[Athenagoras Meridarpax] is the world's leading authority on Cynic philosophy. He runs a mentorship program from Griffith Park in Los Angeles and lives among a nomadic community since 2020 when he lost his trust fund by investing in Game Stop.

	\item[Lyly Scriblerus] is a doctoral student studying literary theory at the University of Hart Knox. She submitted \emph{Down the Doghole} after a particularly productive night of procrastinating on her thesis. 

	\item[Hwyaden Scrimblow, Esq.] is a partner at the law firm Sun, Son, Sunne, \& Sons. When not researching case briefs, he enjoys playing Chess, taking a dip in the pond, and eating breadcrumbs offered by strangers.

	\item[Bily Slon] is an \emph{émigré} from the Czech Republic. He has some qualifications, but the editors could not find anyone who could translate them.

	\item[Charlotte Sneed] was formerly the chief editor at the Blue Yolk Literary Review. She has since retired to an off-grid cabin but continues to type up papers for the Bakhtin Collective on her Royal KMM Typewriter. 

	\item[John Strike]  \blackout{These credentials have been redacted.}  

	\item[Manfu Jinglun Weiss-Mensche] is the head abbot and only monk of the Confusion Daoist School's Mai Property Monestary. He is currently working on a philosophical framework that will synthesize the insights of Buddhism and Computer Science. 

	\item[Unknown] could not be found. 

	\item[Uta Ai] is a virtual Japanese pop star and Internet phenomenon that began as an April Fools' joke. Several hundred songs have been written under her name, which often involve dark and disturbing topics. The most successful of these, ``Die, Die, Die, Die, Die, You Worthless Parasites, You Human Scum,'' charted at the number one spot globably for three months in 2008.  

	

\end{description}
